---
title: "DS202-HW6"
author: "Craig Orman, Ngoc Nguyen"
date: "2/28/2022"
output: html_document
---
Link to the [Github Project](https://github.com/ArgentCode/DS202-HW6 "Github Project")
link to the [homework](https://yumouqiu.github.io/DS202-Spring2022/Practice/practice03.html) is found under the heading '02/28 Lecture 3-4-Practice for dplyr' 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Instaniate stuff
library(tidyverse)
happy <- readRDS("data/HAPPY.rds")
```
### Question 1

Data cleaning: the values “IAP”, “DK” and “NA” all encode missing values. Replace all of these instances by the value NA.

```{r}

# another option
#happy[happy == "IAP"] = NA
#happy[happy == "NA"] = NA
#happy[happy == "DK"] = NA

happy = replace(happy, happy =="IAP", NA)
happy = replace(happy, happy =="NA", NA)
happy = replace(happy, happy =="DK", NA)
```

### Question 2

Check the type of the variable and cast into the right type (factor variable for categorical variables). For age, change “89 OR OLDER” to 89 and assume the variable should be numeric.


happy$HAPPY = as.factor(happy$HAPPY)
happy$AGE[happy$AGE == "89 OR OLDER"] = 89
happy$AGE = as.numeric(happy$AGE)
happy$SEX = as.factor(happy$SEX)
happy$MARITAL = as.factor(happy$MARITAL)
happy$DEGREE = as.factor(happy$DEGREE)
happy$FINRELA = as.factor(happy$FINRELA)
happy$HEALTH = as.factor(happy$HEALTH)
happy$PARTYID = as.factor(happy$PARTYID)
happy$POLVIEWS = as.factor(happy$POLVIEWS)

```{r}

happy = 
  happy %>% mutate(AGE = replace(AGE, AGE == "89 OR OLDER", 89)) %>% 
  mutate(AGE = as.numeric(AGE),
         HAPPY = as.factor(HAPPY),
         SEX = as.factor(SEX),
         MARITAL = as.factor(MARITAL),
         DEGREE = as.factor(DEGREE),
         FINRELA = as.factor(FINRELA),
         HEALTH = as.factor(HEALTH),
         PARTYID = as.factor(PARTYID),
         POLVIEWS = as.factor(POLVIEWS))
```

### Question 3

Bring all levels of factors into a sensible order. For marital you could e.g. order the levels according to average age.

make happy letters small letters
marital is fine
degree needs rework
```{r}

```